Part B-2

### 2024-08-27 msca-pf-part-b1-template.tex
feat: add recommended tags to the template

\section{Excellence}
\label{REL-EVA-RE}

@@

\section{Impact}
\label{IMP-ACT-IA}

@@

\subsection{Suitability and quality of the measures to maximise expected
outcomes and impacts, as set out in the dissemination and exploitation plan,
including communication activities}
\label{COM-DIS-VIS-CDV}

@@

\section{Quality and Efficiency of the Implementation}
\label{WRK-PLA-WP}

@@

\end{document}

>>>>

\textit{The text in each section is provided only as guidance and should be deleted
in the final application (including this text). The tags in the section titles
and at the end of certain sections should be \textbf{kept as is}. They are used for
automatic document processing and are highly recommended by the programme.}

\textit{When in doubt, always consult the official template and programme guide!}

\section{Excellence \mscatag{REL-EVA-RE}}

@@

\section{Impact \mscatag{IMP-ACT-IA}}
\label{IMP-ACT-IA}

@@

\subsection{Suitability and quality of the measures to maximise expected
outcomes and impacts, as set out in the dissemination and exploitation plan,
including communication activities \mscatag{COM-DIS-VIS-CDV}}
\label{COM-DIS-VIS-CDV}

@@

\mscatagend{COM-DIS-VIS-CDV} \mscatagend{IMP-ACT-IA}

\section{Quality and Efficiency of the Implementation
         \mscatag{QUA-LIT-QL} \mscatag{WRK-PLA-WP} \mscatag{CON-SOR-CS} \mscatag{PRJ-MGT-PM}}
\label{WRK-PLA-WP}

@@

\mscatagend{PRJ-MGT-PM} \mscatagend{CON-SOR-CS} \mscatagend{WRK-PLA-WP}
\mscatagend{QUA-LIT-QL}
\end{document}

### 2024-08-27 msca-pf-part-b2-template.tex
feat: add recommended tags to the template

>>>>

\textit{The text in each section is provided only as guidance and should be deleted
in the final application (including this text). However, some of the tables
are part of the document format and should be used and expanded from the ones
provided here.}

\textit{When in doubt, always consult the official template and programme guide!}
